---
title: "Foundations of Data Analytics"
subtitle: Week-5
author: "19BCE1597"
name: "Utplakshi"
date: 24-09-2021
output: html_document
---


##### 1. Install the required Packages
* ggfortify
* ggplot2
* gridExtra
* reshape2
* ggalt
* leaflet
* maps
* ggdendro
* forecast
* any other required packages
```{r, echo=TRUE}
library(ggfortify)
library(ggplot2)
library(gridExtra)
library(reshape2)
library(ggalt)
library(leaflet)
library(maps)
library(ggdendro)
library(forecast)
# install.packages("ggfortify")
# install.packages("ggplot2")
# install.packages("gridExtra")
# install.packages("reshape2")
# install.packages("ggalt")
# install.packages("leaflet")
# install.packages("maps")
# install.packages("ggdendro")
# install.packages("forecast")
```

##### 2. Draw at least one chart(Correlation) for each category given below using any dataset of your choice using R with ggplot2.
* Scatterplot
```{r, echo=TRUE}
library(ggplot2)
Orange
gg<-ggplot(Orange,aes(x=age,y=circumference))+
  geom_point(aes(col=Tree, size=age))+
  geom_smooth(method="loess",se=F)+
  xlim(c(0, 500)) + 
  ylim(c(0, 2000)) + 
  labs(subtitle="Age Vs Circumference", 
       y="Circumference", 
       x="Age", 
       title="Scatterplot")
plot(gg)

```
* Scatterplot With Encircling
```{r, echo=TRUE}
library(ggdendro)
library(ggplot2)
library(gganimate)
library(gapminder)
library(ggExtra)
library(ggcorrplot)
library(scales)
library(ggalt)
library(quantmod)
library(lubridate)

radius<-Orange$circumference/2*pi
Orange
radius_select<-Orange[Orange$radius>100 & Orange$radius<=500& Orange$age>500 & Orange$age<=1000]
age<-Orange$age
#plot
ggplot(Orange, aes(x=age, y=radius)) + 
  geom_point(aes(col=Tree, size=radius)) + # draw points
  geom_smooth(method="loess", se=F) + 
  xlim(c(0, 1000)) + 
  ylim(c(0, 500)) + # draw smoothing line
  geom_encircle(aes(x=age, y=radius), 
                data=radius_select, 
                color="red", 
                size=2, 
                expand=0.08) + # encircle
  labs(subtitle="Age Vs Radius", 
       y="Radius", 
       x="Age", 
       title="Scatterplot + Encircle", 
       caption="Source: Orange")
```
* Jitter Plot
```{r, echo=TRUE}
g <- ggplot(mpg, aes(cty, hwy))
# Jitter Plot
g + geom_point() + 
  geom_smooth(method="lm", se=F) +
  labs(subtitle="mpg: city vs highway mileage", 
       y="hwy", 
       x="cty", 
       title="Jitter Plot", 
       caption="Source: midwest")
```
* Counts Chart
```{r, echo=TRUE}
g <- ggplot(Orange, aes(age, circumference))
g + geom_count(col="tomato3", show.legend=F) +
  labs(subtitle="Orange: age vs circumference", 
       y="Circumference", 
       x="Age", 
       title="Counts Plot")
```
* Bubble Plot
```{r, echo=TRUE}
radius<-Orange$circumference/2*pi
age<-Orange$age
radius_select<-Orange[Orange$radius>100 & Orange$radius<=500& Orange$age>500 & Orange$age<=1000]
g <- ggplot(radius_select, aes(age, radius)) + 
  labs(subtitle="Orange: age vs radius",
       title="Bubble chart")
g + geom_jitter(aes(col=radius, size=age)) + 
  geom_smooth(aes(col=radius), method="lm", se=F)
```
* Correlogram
```{r, echo=TRUE}

# Correlation matrix
data(mtcars)
corr <- round(cor(mtcars), 1)

# Plot
ggcorrplot(corr, hc.order = TRUE, 
           type = "lower", 
           lab = TRUE, 
           lab_size = 3, 
           method="circle", 
           colors = c("tomato2", "white", "springgreen3"), 
           title="Correlogram of mtcars", 
           ggtheme=theme_bw)
```

##### 3. Draw at least one chart(Deviation) for each category given below using any dataset of your choice using R with ggplot2.
* Diverging Bars
```{r, echo=TRUE}
library(ggplot2)

# Data Prep
data("mtcars")  # load data
mtcars$`car name` <- rownames(mtcars)  # create new column for car names
mtcars$mpg_z <- round((mtcars$mpg - mean(mtcars$mpg))/sd(mtcars$mpg), 2)  # compute normalized mpg
mtcars$mpg_type <- ifelse(mtcars$mpg_z < 0, "below", "above")  # above / below avg flag
mtcars <- mtcars[order(mtcars$mpg_z), ]  # sort
mtcars$`car name` <- factor(mtcars$`car name`, levels = mtcars$`car name`)  # convert to factor to retain sorted order in plot.

# Diverging Barcharts
ggplot(mtcars, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
  geom_bar(stat='identity', aes(fill=mpg_type), width=.5)  +
  scale_fill_manual(name="Mileage", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
  labs(subtitle="Normalised mileage from 'mtcars'", 
       title= "Diverging Bars") + 
  coord_flip()
```
* Diverging Lollipop Chart
```{r, echo=TRUE}
ggplot(mtcars, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
  geom_point(stat='identity', fill="black", size=6)  +
  geom_segment(aes(y = 0, 
                   x = `car name`, 
                   yend = mpg_z, 
                   xend = `car name`), 
               color = "black") +
  geom_text(color="white", size=2) +
  labs(title="Diverging Lollipop Chart", 
       subtitle="Normalized mileage from 'mtcars': Lollipop") + 
  ylim(-2.5, 2.5) +
  coord_flip()
```
* Diverging Dot Plot
```{r, echo=TRUE}
theme_set(theme_bw())

# Plot
ggplot(mtcars, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
  geom_point(stat='identity', aes(col=mpg_type), size=6)  +
  scale_color_manual(name="Mileage", 
                     labels = c("Above Average", "Below Average"), 
                     values = c("above"="#00ba38", "below"="#f8766d")) + 
  geom_text(color="white", size=2) +
  labs(title="Diverging Dot Plot", 
       subtitle="Normalized mileage from 'mtcars': Dotplot") + 
  ylim(-2.5, 2.5) +
  coord_flip()
```
* Area Chart
```{r, echo=TRUE}
data("economics", package = "ggplot2")
# Compute % Returns
economics$returns_perc <- c(0, diff(economics$psavert)/economics$psavert[-
                                                                           length(economics$psavert)])
# Create break points and labels for axis ticks
brks <- economics$date[seq(1, length(economics$date), 12)]
lbls <- lubridate::year(economics$date[seq(1, length(economics$date), 12)])
# Plot
ggplot(economics[1:100, ], aes(date, returns_perc)) + 
  geom_area() + 
  scale_x_date(breaks=brks, labels=lbls) + 
  theme(axis.text.x = element_text(angle=90)) + 
  labs(title="Area Chart", 
       subtitle = "Perc Returns for Personal Savings", 
       y="% Returns for Personal savings", 
       caption="Source: economics")
```

##### 4. Draw at least one chart(Ranking) for each category given below using any dataset of your choice using R with ggplot2.
* Ordered Bar Chart
```{r, echo=TRUE}
cty_mpg <- aggregate(mpg$cty, by=list(mpg$manufacturer), FUN=mean)  # aggregate
colnames(cty_mpg) <- c("make", "mileage")  # change column names
cty_mpg <- cty_mpg[order(cty_mpg$mileage), ]  # sort
cty_mpg$make <- factor(cty_mpg$make, levels = cty_mpg$make)  # to retain the order in plot.
head(cty_mpg, 4)
theme_set(theme_bw())

# Draw plot
ggplot(cty_mpg, aes(x=make, y=mileage)) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Ordered Bar Chart", 
       subtitle="Make Vs Avg. Mileage", 
       caption="source: mpg") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
```
* Lollipop Chart
```{r, echo=TRUE}
data("mtcars")  # load data
mtcars$`car name` <- rownames(mtcars)  # create new column for car names
mtcars$mpg_z <- round((mtcars$mpg - mean(mtcars$mpg))/sd(mtcars$mpg), 2)  # compute normalized mpg
mtcars$mpg_type <- ifelse(mtcars$mpg_z < 0, "below", "above")  # above / below avg flag
mtcars <- mtcars[order(mtcars$mpg_z), ]  # sort
mtcars$`car name` <- factor(mtcars$`car name`, levels = mtcars$`car name`)  # convert to factor to retain sorted order in plot.

# Diverging Barcharts
ggplot(mtcars, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
  geom_bar(stat='identity', aes(fill=mpg_type), width=.5)  +
  scale_fill_manual(name="Mileage", 
                    labels = c("Above Average", "Below Average"), 
                    values = c("above"="#00ba38", "below"="#f8766d")) + 
  labs(subtitle="Normalised mileage from 'mtcars'", 
       title= "Diverging Bars") + 
  coord_flip()
```
* Dot Plot
```{r, echo=TRUE}

# Plot
ggplot(mtcars, aes(x=`car name`, y=mpg_z, label=mpg_z)) + 
  geom_point(stat='identity', aes(col=mpg_type), size=6)  +
  scale_color_manual(name="Mileage", 
                     labels = c("Above Average", "Below Average"), 
                     values = c("above"="#00ba38", "below"="#f8766d")) + 
  geom_text(color="white", size=2) +
  labs(title="Diverging Dot Plot", 
       subtitle="Normalized mileage from 'mtcars': Dotplot") + 
  ylim(-2.5, 2.5) +
  coord_flip()
```
* Slope Chart
```{r, echo=TRUE}
# prep data
df <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/gdppercap.csv")
colnames(df) <- c("continent", "1952", "1957")
left_label <- paste(df$continent, round(df$`1952`),sep=", ")
right_label <- paste(df$continent, round(df$`1957`),sep=", ")
df$class <- ifelse((df$`1957` - df$`1952`) < 0, "red", "green")

# Plot
p <- ggplot(df) + geom_segment(aes(x=1, xend=2, y=`1952`, yend=`1957`, col=class), size=.75, show.legend=F) + 
                  geom_vline(xintercept=1, linetype="dashed", size=.1) + 
                  geom_vline(xintercept=2, linetype="dashed", size=.1) +
                  scale_color_manual(labels = c("Up", "Down"), 
                                     values = c("green"="#00ba38", "red"="#f8766d")) +  # color of lines
                  labs(x="", y="Mean GdpPerCap") +  # Axis labels
                  xlim(.5, 2.5) + ylim(0,(1.1*(max(df$`1952`, df$`1957`))))  # X and Y axis limits

# Add texts
p <- p + geom_text(label=left_label, y=df$`1952`, x=rep(1, NROW(df)), hjust=1.1, size=3.5)
p <- p + geom_text(label=right_label, y=df$`1957`, x=rep(2, NROW(df)), hjust=-0.1, size=3.5)
p <- p + geom_text(label="Time 1", x=1, y=1.1*(max(df$`1952`, df$`1957`)), hjust=1.2, size=5)  # title
p <- p + geom_text(label="Time 2", x=2, y=1.1*(max(df$`1952`, df$`1957`)), hjust=-0.1, size=5)  # title

# Minify theme
p + theme(panel.background = element_blank(), 
           panel.grid = element_blank(),
           axis.ticks = element_blank(),
           axis.text.x = element_blank(),
           panel.border = element_blank(),
           plot.margin = unit(c(1,2,1,2), "cm"))
```
* Dumbbell Plot
```{r, echo=TRUE}
health <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/health.csv")
health$Area <- factor(health$Area, levels=as.character(health$Area))  # for right ordering of the dumbells

# health$Area <- factor(health$Area)
gg <- ggplot(health, aes(x=pct_2013, xend=pct_2014, y=Area, group=Area)) + 
  geom_dumbbell(color="#a3c4dc", 
                size=0.75, 
                point.colour.l="#0e668b") + 
  scale_x_continuous(label=percent) + 
  labs(x=NULL, 
       y=NULL, 
       title="Dumbbell Chart", 
       subtitle="Pct Change: 2013 vs 2014", 
       caption="Source: https://github.com/hrbrmstr/ggalt") +
  theme(plot.title = element_text(hjust=0.5, face="bold"),
        plot.background=element_rect(fill="#f7f7f7"),
        panel.background=element_rect(fill="#f7f7f7"),
        panel.grid.minor=element_blank(),
        panel.grid.major.y=element_blank(),
        panel.grid.major.x=element_line(),
        axis.ticks=element_blank(),
        legend.position="top",
        panel.border=element_blank())
plot(gg)
```

##### 5. Draw at least one chart(Composition) for each category given below using any dataset of your choice using R with ggplot2.
* Waffle Chart
```{r, echo=TRUE}
var <- mpg$class  # the categorical data 

## Prep data (nothing to change here)
nrows <- 10
df <- expand.grid(y = 1:nrows, x = 1:nrows)
categ_table <- round(table(var) * ((nrows*nrows)/(length(var))))
categ_table
df$category <- factor(rep(names(categ_table), categ_table))  
# NOTE: if sum(categ_table) is not 100 (i.e. nrows^2), it will need adjustment to make the sum to 100.

## Plot
ggplot(df, aes(x = x, y = y, fill = category)) + 
  geom_tile(color = "black", size = 0.5) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), trans = 'reverse') +
  scale_fill_brewer(palette = "Set3") +
  labs(title="Waffle Chart", subtitle="'Class' of vehicles",
       caption="Source: mpg") + 
  theme(panel.border = element_rect(size = 2),
        plot.title = element_text(size = rel(1.2)),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.position = "right")
```
* Pie Chart
```{r, echo=TRUE}
df <- as.data.frame(table(mpg$class))
colnames(df) <- c("class", "freq")
pie <- ggplot(df, aes(x = "", y=freq, fill = factor(class))) + 
  geom_bar(width = 1, stat = "identity") +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")

pie + coord_polar(theta = "y", start=0)
# Source: Categorical variable.
# mpg$class
pie <- ggplot(mpg, aes(x = "", fill = factor(class))) + 
  geom_bar(width = 1) +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="class", 
       x=NULL, 
       y=NULL, 
       title="Pie Chart of class", 
       caption="Source: mpg")

pie + coord_polar(theta = "y", start=0)
```
* Treemap
```{r, echo=TRUE}
#install.packages("treemapify")
library(treemapify)
proglangs <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/proglanguages.csv")

# plot
ggplot(proglangs, aes(area = value,
                      fill = parent,
                      label = id,
                      subgroup = parent)) +
       geom_treemap() +
			 geom_treemap_subgroup_border() +
			 geom_treemap_subgroup_text(place = "centre",
                                  grow = T,
                                  alpha = 0.5,
                                  colour = "black",
                                  fontface = "italic",
                                  min.size = 0) +
			 geom_treemap_text(colour = "white", place = "topleft", reflow = T)
```
* Bar Chart
```{r, echo=TRUE}
cty_mpg <- aggregate(mpg$cty, by=list(mpg$manufacturer), FUN=mean)  # aggregate
colnames(cty_mpg) <- c("make", "mileage")  # change column names
cty_mpg <- cty_mpg[order(cty_mpg$mileage), ]  # sort
cty_mpg$make <- factor(cty_mpg$make, levels = cty_mpg$make)  # to retain the order in plot.
head(cty_mpg, 4)
theme_set(theme_bw())

# Draw plot
ggplot(cty_mpg, aes(x=make, y=mileage)) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Ordered Bar Chart", 
       subtitle="Make Vs Avg. Mileage", 
       caption="source: mpg") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
```

##### 6. Draw at least one chart(Distribution) for each category given below using any dataset of your choice using R with ggplot2.
* Histogram
```{r, echo=TRUE}
# Histogram on a Continuous (Numeric) Variable
g <- ggplot(mpg, aes(displ)) + scale_fill_brewer(palette = "Spectral")

g + geom_histogram(aes(fill=class), 
                   binwidth = .1, 
                   col="black", 
                   size=.1) +  # change binwidth
  labs(title="Histogram with Auto Binning", 
       subtitle="Engine Displacement across Vehicle Classes")  

g + geom_histogram(aes(fill=class), 
                   bins=5, 
                   col="black", 
                   size=.1) +   # change number of bins
  labs(title="Histogram with Fixed Bins", 
       subtitle="Engine Displacement across Vehicle Classes") 
```
* Density Plot
```{r, echo=TRUE}
# Plot
g <- ggplot(mpg, aes(cty))
g + geom_density(aes(fill=factor(cyl)), alpha=0.8) + 
    labs(title="Density plot", 
         subtitle="City Mileage Grouped by Number of cylinders",
         caption="Source: mpg",
         x="City Mileage",
         fill="# Cylinders")
```
* Box Plot
```{r, echo=TRUE}
g <- ggplot(mpg, aes(class, cty))
g + geom_boxplot(varwidth=T, fill="plum") + 
    labs(title="Box plot", 
         subtitle="City Mileage grouped by Class of vehicle",
         caption="Source: mpg",
         x="Class of Vehicle",
         y="City Mileage")
```
* Dot + Box Plot
```{r, echo=TRUE}
g <- ggplot(mpg, aes(manufacturer, cty))
g + geom_boxplot() + 
  geom_dotplot(binaxis='y', 
               stackdir='center', 
               dotsize = .5, 
               fill="red") +
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Box plot + Dot plot", 
       subtitle="City Mileage vs Class: Each dot represents 1 row in source data",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage")
```
* Tufte Boxplot
```{r, echo=TRUE}
#install.packages("ggthemes")
library(ggthemes)
# plot
g <- ggplot(mpg, aes(manufacturer, cty))
g + geom_tufteboxplot() + 
      theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
      labs(title="Tufte Styled Boxplot", 
           subtitle="City Mileage grouped by Class of vehicle",
           caption="Source: mpg",
           x="Class of Vehicle",
           y="City Mileage")
```
* Violin Plot
```{r, echo=TRUE}
# plot
g <- ggplot(mpg, aes(class, cty))
g + geom_violin() + 
  labs(title="Violin plot", 
       subtitle="City Mileage vs Class of vehicle",
       caption="Source: mpg",
       x="Class of Vehicle",
       y="City Mileage")
```
* Population Pyramid
```{r, echo=TRUE}
email_campaign_funnel <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/email_campaign_funnel.csv")

# X Axis Breaks and Labels 
brks <- seq(-15000000, 15000000, 5000000)
lbls = paste0(as.character(c(seq(15, 0, -5), seq(5, 15, 5))), "m")

# Plot
ggplot(email_campaign_funnel, aes(x = Stage, y = Users, fill = Gender)) +   # Fill column
                              geom_bar(stat = "identity", width = .6) +   # draw the bars
                              scale_y_continuous(breaks = brks,   # Breaks
                                                 labels = lbls) + # Labels
                              coord_flip() +  # Flip axes
                              labs(title="Email Campaign Funnel") +
                              theme_tufte() +  # Tufte theme from ggfortify
                              theme(plot.title = element_text(hjust = .5), 
                                    axis.ticks = element_blank()) +   # Centre plot title
                              scale_fill_brewer(palette = "Dark2")  # Color palette
```

##### 7. Draw at least one chart(Change) for each category given below using any dataset of your choice using R with ggplot2.
* Time Series Plots
```{r, echo=TRUE}
library(ggfortify)


# Plot 
autoplot(AirPassengers) + 
  labs(title="AirPassengers") + 
  theme(plot.title = element_text(hjust=0.5))

```
* Stacked Area Chart
```{r, echo=TRUE}

library(lubridate)


df <- economics[, c("date", "psavert", "uempmed")]
df <- df[lubridate::year(df$date) %in% c(1967:1981), ]

# labels and breaks for X axis text
brks <- df$date[seq(1, length(df$date), 12)]
lbls <- lubridate::year(brks)

# plot
ggplot(df, aes(x=date)) + 
  geom_area(aes(y=psavert+uempmed, fill="psavert")) + 
  geom_area(aes(y=uempmed, fill="uempmed")) + 
  labs(title="Area Chart of Returns Percentage", 
       subtitle="From Wide Data format", 
       caption="Source: Economics", 
       y="Returns %") +  # title and caption
  scale_x_date(labels = lbls, breaks = brks) +  # change to monthly ticks and labels
  scale_fill_manual(name="", 
                    values = c("psavert"="#00ba38", "uempmed"="#f8766d")) +  # line color
  theme(panel.grid.minor = element_blank())  # turn off minor grid
```
* Calendar Heat Map
```{r, echo=TRUE}
library(plyr)
library(scales)
library(zoo)

df <- read.csv("https://raw.githubusercontent.com/selva86/datasets/master/yahoo.csv")
df$date <- as.Date(df$date)  # format date
df <- df[df$year >= 2012, ]  # filter reqd years

# Create Month Week
df$yearmonth <- as.yearmon(df$date)
df$yearmonthf <- factor(df$yearmonth)
df <- ddply(df,.(yearmonthf), transform, monthweek=1+week-min(week))  # compute week number of month
df <- df[, c("year", "yearmonthf", "monthf", "week", "monthweek", "weekdayf", "VIX.Close")]

# Plot
ggplot(df, aes(monthweek, weekdayf, fill = VIX.Close)) + 
  geom_tile(colour = "white") + 
  facet_grid(year~monthf) + 
  scale_fill_gradient(low="red", high="green") +
  labs(x="Week of Month",
       y="",
       title = "Time-Series Calendar Heatmap", 
       subtitle="Yahoo Closing Price", 
       fill="Close")
```
* Slope Chart
```{r, echo=TRUE}
library(dplyr)
source_df <- read.csv("https://raw.githubusercontent.com/jkeirstead/r-slopegraph/master/cancer_survival_rates.csv")

# Define functions. Source: https://github.com/jkeirstead/r-slopegraph
tufte_sort <- function(df, x="year", y="value", group="group", method="tufte", min.space=0.05) {
    ## First rename the columns for consistency
    ids <- match(c(x, y, group), names(df))
    df <- df[,ids]
    names(df) <- c("x", "y", "group")

    ## Expand grid to ensure every combination has a defined value
    tmp <- expand.grid(x=unique(df$x), group=unique(df$group))
    tmp <- merge(df, tmp, all.y=TRUE)
    df <- mutate(tmp, y=ifelse(is.na(y), 0, y))
  
    ## Cast into a matrix shape and arrange by first column
    require(reshape2)
    tmp <- dcast(df, group ~ x, value.var="y")
    ord <- order(tmp[,2])
    tmp <- tmp[ord,]
    
    min.space <- min.space*diff(range(tmp[,-1]))
    yshift <- numeric(nrow(tmp))
    ## Start at "bottom" row
    ## Repeat for rest of the rows until you hit the top
    for (i in 2:nrow(tmp)) {
        ## Shift subsequent row up by equal space so gap between
        ## two entries is >= minimum
        mat <- as.matrix(tmp[(i-1):i, -1])
        d.min <- min(diff(mat))
        yshift[i] <- ifelse(d.min < min.space, min.space - d.min, 0)
    }

    
    tmp <- cbind(tmp, yshift=cumsum(yshift))

    scale <- 1
    tmp <- melt(tmp, id=c("group", "yshift"), variable.name="x", value.name="y")
    ## Store these gaps in a separate variable so that they can be scaled ypos = a*yshift + y

    tmp <- transform(tmp, ypos=y + scale*yshift)
    return(tmp)
   
}

plot_slopegraph <- function(df) {
    ylabs <- subset(df, x==head(x,1))$group
    yvals <- subset(df, x==head(x,1))$ypos
    fontSize <- 3
    gg <- ggplot(df,aes(x=x,y=ypos)) +
        geom_line(aes(group=group),colour="grey80") +
        geom_point(colour="white",size=8) +
        geom_text(aes(label=y), size=fontSize, family="American Typewriter") +
        scale_y_continuous(name="", breaks=yvals, labels=ylabs)
    return(gg)
}    

## Prepare data    
df <- tufte_sort(source_df, 
                 x="year", 
                 y="value", 
                 group="group", 
                 method="tufte", 
                 min.space=0.05)

df <- transform(df, 
                x=factor(x, levels=c(5,10,15,20), 
                            labels=c("5 years","10 years","15 years","20 years")), 
                y=round(y))

## Plot
plot_slopegraph(df) + labs(title="Estimates of % survival rates") + 
                      theme(axis.title=element_blank(),
                            axis.ticks = element_blank(),
                            plot.title = element_text(hjust=0.5,
                                                      family = "American Typewriter",
                                                      face="bold"),
                            axis.text = element_text(family = "American Typewriter",
                                                     face="bold"))
```
* Seasonal Plot
```{r, echo=TRUE}
library(forecast)
theme_set(theme_classic())

# Subset data
nottem_small <- window(nottem, start=c(1920, 1), end=c(1925, 12))  # subset a smaller timewindow

# Plot
ggseasonplot(AirPassengers) + labs(title="Seasonal plot: International Airline Passengers")
```

##### 8. Draw at least one chart(groups) for each category given below using any dataset of your choice using R with ggplot2.
* Dendrogram
```{r, echo=TRUE}

hc <- hclust(dist(USArrests), "ave")  # hierarchical clustering
# plot
ggdendrogram(hc, rotate = TRUE, size = 2)
```
* Clusters
```{r, echo=TRUE}
df <- iris[c(1, 2, 3, 4)]
pca_mod <- prcomp(df)  # compute principal components

# Data frame of principal components ----------------------
df_pc <- data.frame(pca_mod$x, Species=iris$Species)  # dataframe of principal components
df_pc_vir <- df_pc[df_pc$Species == "virginica", ]  # df for 'virginica'
df_pc_set <- df_pc[df_pc$Species == "setosa", ]  # df for 'setosa'
df_pc_ver <- df_pc[df_pc$Species == "versicolor", ]  # df for 'versicolor'
 
# Plot ----------------------------------------------------
ggplot(df_pc, aes(PC1, PC2, col=Species)) + 
  geom_point(aes(shape=Species), size=2) +   # draw points
  labs(title="Iris Clustering", 
       subtitle="With principal components PC1 and PC2 as X and Y axis",
       caption="Source: Iris") + 
  coord_cartesian(xlim = 1.2 * c(min(df_pc$PC1), max(df_pc$PC1)), 
                  ylim = 1.2 * c(min(df_pc$PC2), max(df_pc$PC2))) +   # change axis limits
  geom_encircle(data = df_pc_vir, aes(x=PC1, y=PC2)) +   # draw circles
  geom_encircle(data = df_pc_set, aes(x=PC1, y=PC2)) + 
  geom_encircle(data = df_pc_ver, aes(x=PC1, y=PC2))
```

##### 9. Draw at least one chart(Spatial) for each category given below using any dataset of your choice using R with ggplot2.
* Open Street Map
```{r, echo=TRUE}
library(leaflet)
options(nextjournal.display.htmlwidgetsEnabled=TRUE)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
```
* Google Road Map
```{r, echo=TRUE}
library(maps)

mapStates <- map("state", fill = TRUE, plot = FALSE)

leaflet(data = mapStates) %>% 
	addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)
```
* Google Hybrid Map
```{r, echo=TRUE}
m <- leaflet(mapStates) %>%
  setView(-96, 37.8, 4) %>%
  addTiles() %>%
  addPolygons()
m
```

##### You reached to the end of the document, knit the worked out document into html format and uplaod the html file. 
```{r, echo=FALSE}
print(Sys.time())
print(Sys.getenv("COMPUTERNAME"))
print(Sys.getenv("USERNAME"))
```