---
title: "Foundations of Data Analytics"
subtitle: Week-7
author: "19BCE1597-Utplakshi"
date: 08-10-2021
output: html_document
---
```{r, echo=TRUE}
defaultW <- getOption("warn") 
options(warn = -1) 
options(warn = defaultW)
```
##### 1. load and display the file named Demo.csv file.

```{r, echo=TRUE}
demo<-read.csv('E:/Datasets/Demo.csv',header=T)
demo
```

##### 2. Find the slope and intercept of the regression equation by considering  `x` as the predictor and `y` as the target.
```{r, echo=TRUE}
mean_x = mean(demo$x)
mean_y = mean(demo$y)

demo$x1 = demo$x - mean_x
demo$y1 = demo$y - mean_y

demo$x11 = demo$x1 * demo$x1
demo$xy = demo$x1 * demo$y1

b1 = sum(demo$xy ) / sum(demo$x11)
b1

b0 = mean_y - b1*mean_x
b0
```
 
##### 3. use the lm() function and fit the regression equation on the loaded data and check whether it is aligned with step2 or not. 
```{r, echo=TRUE}
model <- lm(y ~ x, data=demo)
model
```

##### 4. load advertisement.csv data set and display the top 10 records in that.
```{r, echo=TRUE}
ad<-read.csv('E:/Datasets/Advertising.csv',header=T)
head(ad,n=10)
```

##### 5. Find the relationship between Sales w.r.t TV by plotting a scatter plot with a regression line.

```{r, echo=TRUE}
r1 <- lm(Sales~TV, data=ad)
with(ad, plot(TV, Sales))
abline(r1)
```

##### 6. Find the relationship between Sales w.r.t Newspaper by plotting a scatter plot with a regression line. 
 
```{r, echo=TRUE}
r2 <- lm(Sales~Newspaper, data=ad)
with(ad, plot(Newspaper, Sales))
abline(r2)
```

##### 7. Find the relationship between Sales w.r.t Radio by plotting a scatter plot with a regression line.
```{r, echo=TRUE}
r3 <- lm(Sales~Radio, data=ad)
with(ad, plot(Radio, Sales))
abline(r3)
```

##### 8. Write down your inferences from the above three plots.
```{r, echo=TRUE}
print("Both TV and Radio have a positive linear correlation with the sales attribute. From the above graphs, TV is has more correlation to Sales than Radio and Newspaper.")
```

##### 9. Construct an appropriate plot to detect outliers in TV column.
```{r, echo=TRUE}
boxplot(ad$TV)
```

##### 10. Construct an appropriate plot to detect outliers in Newspaper column.
```{r, echo=TRUE}
boxplot(ad$Newspaper)

```
##### 11. Construct an appropriate plot to detect outliers in Radio column.
```{r, echo=TRUE}
boxplot(ad$Radio)

```
##### 12. Find the correlation coefficent of Sales with other three variables and write down your observations.  
```{r, echo=TRUE}
cor(ad$Sales, ad$TV)
cor(ad$Sales, ad$Radio)
cor(ad$Sales, ad$Newspaper)

print("Sales and Tv are highly correlated. Correlational coefficient is greater than ) i.e positive for all variables signifies that all of them has a positive relationship with sales. i.e the move in the same direction as sales")
```

##### 13. Build a Linear Regression Model on Sales w.r.t TV column and display the coefficents.

```{r, echo=TRUE}
r1 <- lm(Sales~TV, data=ad)
r1$coefficients
```

##### 14. check whether the created linear model to be statistically significant or not. 

```{r, echo=TRUE}
summary(r1)
print("As the p-value is much less than 0.05, we reject the null hypothesis that β = 0. Hence there is a significant relationship between the variables in the linear regression model of the data set faithful.")
```
##### 15. Validate the assumptions of the linear regression model for the given dataset. 
```{r, echo=TRUE}
#Create the diagnostic plots using ggfortify
library(ggfortify)
reg1 <- lm(Sales~TV, data=ad)
autoplot(reg1)
head(reg1,4)
#Creating plots using plot function
#Linearity of the data
plot(reg1, 1)
#Homogeneity of variance
plot(reg1,2)
#Normality of residuals
plot(reg1,3)
# Cook's distance
plot(reg1,4)
# Residuals vs Leverage
plot(reg1, 5)

```

##### You reached to the end of the document, knit the worked out document into html format and uplaod the html file. 
```{r, echo=TRUE}
print(Sys.time())
print(Sys.getenv("COMPUTERNAME"))
print(Sys.getenv("USERNAME"))
```