---
title: "Foundations of Data Analytics"
subtitle: Week-8
author: "19BCE1597-Utplakshi"
date: 15-10-2021
output: html_document
---

##### 1. Given an integer `n`, perform the following conditional actions:
* If `n` is odd, print  Weird
* If`n` is even and in the inclusive range of `2`  to `5`, print  Not Weird
* If `n` is even and in the inclusive range of `6`  to  `20`, print  Weird
* If `n` is even and greater than `20`, print  Not Weird.

```{r, echo=FALSE}
n = 27
if(n%%2==1) {
  print("Weird")
} else {
  if(n>=2 && n<=5) {
    print("Not Weird")
  } else if(n>=6 && n<=20) {
    print("Weird")
  } else{
    print("Not Weird")
  }
}
```

##### 2. Given a vehicle reg. no. `n`, perform the following conditional actions: 
* if the last 4 digits of the vehicle no. is `odd` and 'non-prime' print `vehicle is allowed on Saturday and Sunday`.
* if the last 4 digits of the vehicle no. is `even` print `vehicle is allowed on Monday and Tuesday`.
* if the last 4 digits of the vehicle no. is `odd` and 'prime' print `vehicle is allowed on Wednesday to Thursday`.
```{r, echo=FALSE}
isPrime <- function(num) {
  flag = 0
  if(num > 1) {
    flag = 1
    for(i in 2:(num-1)) {
      if ((num %% i) == 0) {
        flag = 0
        break
      }
    }
  } 
  if(num == 2)
    flag = 1
  if(flag == 1) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}

N = 3
if (N%%2==1 & !isPrime(N)) {
  print("Vehicle is allowed on Saturday and Sunday")
} else if (N%%2==0) {
  print("Vehicle is allowed on Monday and Tuesday")
} else if (N%%2==1 & isPrime(N)) {
  print("Vehicle is allowed on Wednesday to Thursday")
}
```
 
##### 3. Read your full name and print the number of vowels and consonants present in your name. 
```{r, echo=FALSE}
name = "Utplakshi"
get_count <- function(input_str){
  split_str <- strsplit(input_str, "")[[1]]
  vowellist <- c("a", "e", "i", "o", "u")
  charcount <- 0 
  constcount <- 0
  for (character in split_str){
    if (character %in% vowellist){
        charcount <- charcount + 1
    } else if(character!=' '){
      constcount <- constcount+1
    }
  }
  print(charcount)
  print(constcount)
}
get_count(name)
```

##### 4. Check the password is valid or not based on password policies mention below:
* Password should not contain any space.
* Password should contain at least one digit(0-9).
* Password length should be between 8 to 15 characters.
* Password should contain at least one lowercase letter(a-z).
* Password should contain at least one uppercase letter(A-Z).
* Password should contain at least one special character ( @, #, %, &, !, $, etc….).
```{r, echo=FALSE}
space <- c(' ')
spc <- c("@","#","%","!","$")
low <- strsplit(intToUtf8(97:122), '')[[1]]
up <- strsplit(intToUtf8(65:90), '')[[1]]
num <- c(0:9)

isCheckOne <- function(str, arr) {
  flag = 0
  for (i in str) {
    if(i %in% arr) {
      flag = 1
      break
    }
  }
  if(flag==1) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}

str <- strsplit("UtplakshiS@13", '')[[1]]
if(length(str)>=8 & length(str)<=15 & (isCheckOne(str, spc)) & (isCheckOne(str, low)) & (isCheckOne(str, up)) &(isCheckOne(str, num))) {
  print("Password is Valid")
} else {
  print("Password is invalid")
}
```

##### 5. Find the strength of the password. Let a strong password is one that satisfies all the below conditions. A moderate password is one that satisfies first three conditions and has length at least `6`, otherwise password is week. 
* It contains at least one lowercase English character.
* It contains at least one uppercase English character.
* It contains at least one special character. The special characters are: !@#$%^&*()-+
* Its length is at least 8.
* It contains at least one digit.
```{r, echo=FALSE}
spc <- c("!","@","#","%","$","^","*","(",")","-","+")
low <- strsplit(intToUtf8(97:122), '')[[1]]
up <- strsplit(intToUtf8(65:90), '')[[1]]
num <- c(0:9)

isCheckOne <- function(str, arr) {
  flag = 0
  for (i in str) {
    if(i %in% arr) {
      flag = 1
      break
    }
  }
  if(flag==1) {
    return(TRUE)
  } else {
    return(FALSE)
  }
}

pwd <- strsplit("UtplakshiS@13", '')[[1]]
if(length(pwd)>=8 & (isCheckOne(pwd, low)) & (isCheckOne(pwd, up)) &(isCheckOne(pwd, num))) {
  print("Password is Strong")
} else {
  print("Password is Weak")
}
```

##### 6. Read your full name and print the unique characters present in your name. 
 
```{r, echo=FALSE}
uniqchars <- function(x) {
  unique(strsplit(x, "")[[1]])
}
uniqchars("Utplakshi")
```

##### 7. Read your date of birth and print your age on today.
```{r, echo=FALSE}
dob = "2000-09-30"
currentAge = difftime(Sys.Date(),dob, units = "weeks")
num = as.integer(currentAge)
print(paste("The current age is ",num/52.25, " years"))
```

##### 8. Generate  a sequence from 1 to 100 and print "Hop" for multiples of 3, print "Pop" for multiples of 5, and print "HopPop" for multiples of bth 3 and 5.
```{r, echo=FALSE}
for(i in 1:100) {
  if(i%%3==0 & i%%5==0) {
    print("HopPop")
  } else if(i%%3==0) {
    print("Hop")
  } else if(i%%5==0) {
    print("Pop")
  } else {
    print(i)
  }
}
```

##### 9. Generate a sequence of 26 alphabets and print first 10 characters in lower case and last 10 characters in upper case and make letters between 13th to 15th are in upper case.
```{r, echo=FALSE}
vec <- 97:122
count = 1
for(x in vec) {
  if(count<=10) {
    print(intToUtf8(x))
  } else if(count>=13 & count<=15) {
    print(toupper(intToUtf8(x)))
  } else if(x>=17) {
    print(toupper(intToUtf8(x)))
  }
  count=count+1
}
```

##### 10. Given a number, write a function  to decide it is a perfect number or not. 
```{r, echo=FALSE}
n = 28
i = 1
s = 0
while (i < n) {
      if (n %% i == 0) {
        s = s + i
      }
      i = i + 1
}
if (s == n) {
      print(paste(n,"is a perfect number"))
    } else{
      print(paste(n,"is not a perfect number"))
    }
```
##### 11. Given a number, write r script to print the pairwise factors of the given number.
```{r, echo=FALSE}
n = 100
m = 0
if(n%%2 == 0){
  m = n/2
} else{
  m = (n+1)/2
}
for(i in 1 : m){
  if(n%%i == 0){
    print(paste(i, " ", n/i))
  }
}
```
##### 12. Write a program to find all the credentials(list) of the resume present in the job post(list) or not.  
```{r, echo=FALSE}
jobPostKeyword<-c("Java","C","Hero","Web Developer","Ruby")
personsResumeKeyword<-c("Java","Cpp","Ruby","Python","C","Web Developer")
cnt=0
for(i in jobPostKeyword){
  for (j in personsResumeKeyword) {
    if(i==j){
      cnt=cnt+1
      break
      }
    else
      next
  }
}
if(cnt==length(jobPostKeyword)){
  print("Yes person is elgible for job")}else
  print("No person is not eligible")
```

##### 13. Given a vector, print the number of `NA` values present in the vector using a function. 

```{r, echo=FALSE}
count_NA<-function(v){
  count=0
  for(i in v){
    if(is.na(i)==TRUE)
      count=count+1
  }
  return(count)
}
v<-c(1,NA,3,NA,1,NA,7)
print("The number of NA values in vector")
print(count_NA(v))
```

##### 14. Given a string, print `yes` if number of vowels are greater than consonants in the given string else `no` using a function. 

```{r, echo=FALSE}
vowels = c('a','e','i','o','u')

isGreater = function(str){
  s = tolower(str)
  count=0
  for(c in s){
    if (c %in% vowels){
      count= count + 1
    }
  }
  return(count)
}

isGreater2 = function(str){
  return( length(str) - isGreater(str))
}

name = "Utplakshi"
nv = isGreater(name)
nc = isGreater2(name)
print(paste("String:",name))
if(nv>nc){
  print("yes")
}else{
  print("no")
}
```
##### 15. Read your full name in lower case, write R script to casefold all the first letters of the word in upper case.   
```{r, echo=FALSE}
funcc = function(str){
  str = strsplit(str,"")[[1]]
  n_str=""
  for(i in seq_along(str)){
    if(i==1 || str[i-1]==" "){
      n_str = paste(n_str,toupper(str[i]),sep = "")
    }else{
      n_str = paste(n_str,str[i],sep = "")
    }
  }
  print(n_str)
}

funcc("Utplakshi")
```

##### You reached to the end of the document, knit the worked out document into html format and uplaod the html file. 
```{r, echo=TRUE}
print(Sys.time())
print(Sys.getenv("COMPUTERNAME"))
print(Sys.getenv("USERNAME"))
```