---
title: "lab6.rmd"
author: "utplakshi"
date: "11/10/2021"
output: html_document
---

```{r, echo=TRUE}
defaultW <- getOption("warn") 
options(warn = -1) 
options(warn = defaultW)
```

Consider the COVID-19 pandemic situation. Analysis and forcast the pandemic trend by 
using Covid19 dataset 
1. You want to predict the last year monthly, weekly trend based on the RTPCR response, 
(i.e) No. of +Ve cases and No. –Ve cases along with admitted and discharged trend.
2. Identify the deathrate due to Covid-19
3. Compare the last year and this year trend and forcast the 3rd Wave impact in India
4. Construct the model using the Simple moving average, Exponential Moving Average 
and ARIMA to forcast the Covid19 Dataset.
5. Show the all above implementation with the visual impact

```{r, echo=TRUE}
######## Q1 ########
library(dplyr)
library(janitor)
TEST <- read.table("E:/Datasets/StatewiseTestingDetails.csv", header=T, sep=",")
head(TEST)
nrow(TEST)
TEST <- TEST[!is.na(TEST$TotalSamples), ]
nrow(TEST)
head(TEST)
tail(TEST)
TEST <- TEST[order(TEST$Date),]
row.names(TEST) <- NULL
head(TEST)
nrow(TEST)
####################  RTPCR rate using all models ###################
RTPCR_df <- data.frame(TEST$Date, TEST$TotalSamples)
head(RTPCR_df)
tail(RTPCR_df)
RTPCR_df <- aggregate(RTPCR_df["TEST.TotalSamples"], by=RTPCR_df["TEST.Date"], sum)
head(RTPCR_df)
tail(RTPCR_df)
#################### Monthly  RTPCR rate using all models ###################
#Simple Movie Average
RTPCR_df_timeseries<-  ts(RTPCR_df$TEST.TotalSamples, freq=12 ,  start=c(2020, 4), end=c(2021, 8))
head(RTPCR_df_timeseries)
class(RTPCR_df_timeseries)
RTPCR_df_timeseries
plot.ts(RTPCR_df_timeseries)
library("TTR")
RTPCR_df_timeseries_SMA <- SMA(RTPCR_df_timeseries,n=1)
RTPCR_df_timeseries_SMA
plot.ts(RTPCR_df_timeseries_SMA)
#Exponential Smoothing 
RTPCR_smooth <- HoltWinters(RTPCR_df_timeseries, beta=FALSE, gamma=FALSE)
RTPCR_smooth$fitted
plot(RTPCR_smooth)
RTPCR_smooth$SSE
HoltWinters(RTPCR_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
RTPCR_forcast <- forecast:::forecast.HoltWinters(RTPCR_smooth, h=8)
RTPCR_forcast
# Arima :-
plot(RTPCR_df_timeseries)
#This will plot the time series
abline(reg=lm(RTPCR_df_timeseries~time(RTPCR_df_timeseries)))
cycle(RTPCR_df_timeseries)
#plot(aggregate(RTPCR_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(RTPCR_df_timeseries~cycle(RTPCR_df_timeseries))
acf(log(RTPCR_df_timeseries))
pacf(diff(log(RTPCR_df_timeseries)))
(fit <- arima(log(RTPCR_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(RTPCR_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#################### Weekely  RTPCR  rate using all models ###################
#Simple Movie Average
RTPCR_df_timeseries<-  ts(RTPCR_df$TEST.TotalSamples, freq=52 ,  start=c(2020, 4), end=c(2021, 8))
head(RTPCR_df_timeseries)
class(RTPCR_df_timeseries)
RTPCR_df_timeseries
plot.ts(RTPCR_df_timeseries)
library("TTR")
RTPCR_df_timeseries_SMA <- SMA(RTPCR_df_timeseries,n=1)
RTPCR_df_timeseries_SMA
plot.ts(RTPCR_df_timeseries_SMA)
#Exponential Smoothing 
RTPCR_smooth <- HoltWinters(RTPCR_df_timeseries, beta=FALSE, gamma=FALSE)
RTPCR_smooth$fitted
plot(RTPCR_smooth)
RTPCR_smooth$SSE
HoltWinters(RTPCR_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
RTPCR_forcast <- forecast:::forecast.HoltWinters(RTPCR_smooth, h=8)
RTPCR_forcast
# Arima :-
plot(RTPCR_df_timeseries)
#This will plot the time series
abline(reg=lm(RTPCR_df_timeseries~time(RTPCR_df_timeseries)))
cycle(RTPCR_df_timeseries)
#plot(aggregate(RTPCR_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(RTPCR_df_timeseries~cycle(RTPCR_df_timeseries))

acf(log(RTPCR_df_timeseries))
pacf(diff(log(RTPCR_df_timeseries)))
(fit <- arima(log(RTPCR_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(RTPCR_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))



TEST <- read.table("E:/Datasets/StatewiseTestingDetails.csv", header=T, sep=",")
#E:/Datasets/StatewiseTestingDetails.csv
head(TEST)
nrow(TEST)
TEST <- TEST[!is.na(TEST$Positive), ]
nrow(TEST)
head(TEST)
tail(TEST)
TEST <- TEST[order(TEST$Date),]
row.names(TEST) <- NULL
head(TEST)
nrow(TEST)
####################  positivity rate using all models ###################
Positive_df <- data.frame(TEST$Date, TEST$Positive)
head(Positive_df)
tail(Positive_df)
Positive_df <- aggregate(Positive_df["TEST.Positive"], by=Positive_df["TEST.Date"], sum)
head(Positive_df)
tail(Positive_df)
#################### Monthly  positivity rate using all models ###################
#Simple Movie Average

Positive_df_timeseries<-  ts(Positive_df$TEST.Positive, freq=12 ,  start=c(2020, 4), end=c(2021, 8))
head(Positive_df_timeseries)
class(Positive_df_timeseries)
Positive_df_timeseries
plot.ts(Positive_df_timeseries)
library("TTR")
Positive_df_timeseries_SMA <- SMA(Positive_df_timeseries,n=1)
Positive_df_timeseries_SMA
plot.ts(Positive_df_timeseries_SMA)
#Exponential Smoothing 
Positive_smooth <- HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE)
Positive_smooth$fitted
plot(Positive_smooth)
Positive_smooth$SSE
HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Positive_forcast <- forecast:::forecast.HoltWinters(Positive_smooth, h=8)
Positive_forcast
# Arima :-
plot(Positive_df_timeseries)
#This will plot the time series
abline(reg=lm(Positive_df_timeseries~time(Positive_df_timeseries)))
cycle(Positive_df_timeseries)
#plot(aggregate(Positive_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Positive_df_timeseries~cycle(Positive_df_timeseries))
acf(log(Positive_df_timeseries))
pacf(diff(log(Positive_df_timeseries)))
(fit <- arima(log(Positive_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Positive_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#################### Weekly  positive rate using all models ###################
#Simple Movie Average
Positive_df_timeseries<-  ts(Positive_df$TEST.Positive, freq=52 ,  start=c(2020, 4), end=c(2021, 8))
head(Positive_df_timeseries)
class(Positive_df_timeseries)
Positive_df_timeseries
plot.ts(Positive_df_timeseries)
library("TTR")
Positive_df_timeseries_SMA <- SMA(Positive_df_timeseries,n=1)
Positive_df_timeseries_SMA
plot.ts(Positive_df_timeseries_SMA)
# Exponential Smoothing
Positive_smooth <- HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE)
Positive_smooth$fitted
plot(Positive_smooth)
Positive_smooth$SSE
HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Positive_forcast <- forecast:::forecast.HoltWinters(Positive_smooth, h=8)
Positive_forcast
# Arima :-
plot(Positive_df_timeseries)
#This will plot the time series
abline(reg=lm(Positive_df_timeseries~time(Positive_df_timeseries)))
cycle(Positive_df_timeseries)
#plot(aggregate(Positive_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Positive_df_timeseries~cycle(Positive_df_timeseries))
acf(log(Positive_df_timeseries))
pacf(diff(log(Positive_df_timeseries)))
(fit <- arima(log(Positive_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 8*7)
pred
ts.plot(Positive_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
library(dplyr)
library(janitor)
TEST <- read.table("E:/Datasets/StatewiseTestingDetails.csv", header=T, sep=",")
head(TEST)
nrow(TEST)
TEST <- TEST[!is.na(TEST$Negative), ]
nrow(TEST)
head(TEST)
tail(TEST)
TEST <- TEST[order(TEST$Date),]
row.names(TEST) <- NULL
head(TEST)
nrow(TEST)
####################  Negative rate using all models ###################
Negative_df <- data.frame(TEST$Date, TEST$Negative)
head(Negative_df)
tail(Negative_df)
Negative_df <- aggregate(Negative_df["TEST.Negative"], by=Negative_df["TEST.Date"], sum)
head(Negative_df)
tail(Negative_df)
#################### Monthly  Negative rate using all models ###################
#Simple Movie Average
Negative_df_timeseries<-  ts(Negative_df$TEST.Negative, freq=12 ,  start=c(2020, 4), end=c(2021, 8))
head(Negative_df_timeseries)
class(Negative_df_timeseries)
Negative_df_timeseries
plot.ts(Negative_df_timeseries)
library("TTR")
Negative_df_timeseries_SMA <- SMA(Negative_df_timeseries,n=1)
Negative_df_timeseries_SMA
plot.ts(Negative_df_timeseries_SMA)
#Exponential Smoothing 
Negative_smooth <- HoltWinters(Negative_df_timeseries, beta=FALSE, gamma=FALSE)
Negative_smooth$fitted
plot(Negative_smooth)
Negative_smooth$SSE
HoltWinters(Negative_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Negative_forcast <- forecast:::forecast.HoltWinters(Negative_smooth, h=8)
Negative_forcast
# Arima :-
plot(Negative_df_timeseries)
#This will plot the time series
abline(reg=lm(Negative_df_timeseries~time(Negative_df_timeseries)))
cycle(Negative_df_timeseries)
#plot(aggregate(Negative_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Negative_df_timeseries~cycle(Negative_df_timeseries))
acf(log(Negative_df_timeseries))
pacf(diff(log(Negative_df_timeseries)))
(fit <- arima(log(Negative_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Negative_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#################### Weekly  Negative rate using all models ###################
#Simple Movie Average
Negative_df_timeseries<-  ts(Negative_df$TEST.Negative, freq=52 ,  start=c(2020, 4), end=c(2021, 8))
head(Negative_df_timeseries)
class(Negative_df_timeseries)
Negative_df_timeseries
plot.ts(Negative_df_timeseries)
library("TTR")
Negative_df_timeseries_SMA <- SMA(Negative_df_timeseries,n=1)
Negative_df_timeseries_SMA
plot.ts(Negative_df_timeseries_SMA)
# Exponential Smoothing
Negative_smooth <- HoltWinters(Negative_df_timeseries, beta=FALSE, gamma=FALSE)
Negative_smooth$fitted
plot(Negative_smooth)
Negative_smooth$SSE
HoltWinters(Negative_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Negative_forcast <- forecast:::forecast.HoltWinters(Negative_smooth, h=8)
Negative_forcast
# Arima :-
plot(Negative_df_timeseries)
#This will plot the time series
abline(reg=lm(Negative_df_timeseries~time(Negative_df_timeseries)))
cycle(Negative_df_timeseries)
#plot(aggregate(Negative_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Negative_df_timeseries~cycle(Negative_df_timeseries))
acf(log(Negative_df_timeseries))
pacf(diff(log(Negative_df_timeseries)))
(fit <- arima(log(Negative_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Negative_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#####Q2. ########
library(dplyr)
library(janitor)
COVID_19 <- read.table("E:/Datasets/covid_19_india.csv", header=T, sep=",")
head(COVID_19)
nrow(COVID_19)
COVID_19[COVID_19 == '-'] <- NA  
COVID_19[COVID_19 == 0] <- NA 
COVID_19 <- COVID_19[!is.na(COVID_19$Deaths), ]
nrow(COVID_19)
head(COVID_19)
tail(COVID_19)
COVID_19 <- COVID_19[order(COVID_19$Date),]
row.names(COVID_19) <- NULL
head(COVID_19)
nrow(COVID_19)
####################  Death rate using all models ###################
Death_df <- data.frame(COVID_19$Date, COVID_19$Deaths)
head(Death_df)
tail(Death_df)

Death_df <- aggregate(Death_df["COVID_19.Deaths"], by=Death_df["COVID_19.Date"], sum)
head(Death_df)
tail(Death_df)
#################### Monthly  Death rate using all models ###################
#Simple Movie Average
Death_df_timeseries<-  ts(Death_df$COVID_19.Deaths, freq=12 ,  start=c(2020, 4), end=c(2021, 8))
head(Death_df_timeseries)
class(Death_df_timeseries)
Death_df_timeseries
plot.ts(Death_df_timeseries)
library("TTR")
Death_df_timeseries_SMA <- SMA(Death_df_timeseries,n=1)
Death_df_timeseries_SMA
plot.ts(Death_df_timeseries_SMA)
#Exponential Smoothing 
Death_smooth <- HoltWinters(Death_df_timeseries, beta=FALSE, gamma=FALSE)
Death_smooth$fitted
plot(Death_smooth)
Death_smooth$SSE
HoltWinters(Death_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Death_forcast <- forecast:::forecast.HoltWinters(Death_smooth, h=8)
Death_forcast
# Arima :-
plot(Death_df_timeseries)
#This will plot the time series
abline(reg=lm(Death_df_timeseries~time(Death_df_timeseries)))
cycle(Death_df_timeseries)
#plot(aggregate(Death_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Death_df_timeseries~cycle(Death_df_timeseries))
acf(log(Death_df_timeseries))
pacf(diff(log(Death_df_timeseries)))
(fit <- arima(log(Death_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Death_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#################### Weekly  Death  rate using all models ###################
#Simple Movie Average
Death_df_timeseries<-  ts(Death_df$COVID_19.Deaths, freq=52 ,  start=c(2020, 4), end=c(2021, 8))
head(Death_df_timeseries)
class(Death_df_timeseries)
Death_df_timeseries
plot.ts(Death_df_timeseries)
library("TTR")
Death_df_timeseries_SMA <- SMA(Death_df_timeseries,n=1)
Death_df_timeseries_SMA
plot.ts(Death_df_timeseries_SMA)
#Exponential Smoothing 
Death_smooth <- HoltWinters(Death_df_timeseries, beta=FALSE, gamma=FALSE)
Death_smooth$fitted
plot(Death_smooth)
Death_smooth$SSE
HoltWinters(Death_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Death_forcast <- forecast:::forecast.HoltWinters(Death_smooth, h=8)
Death_forcast
# Arima :-
plot(Death_df_timeseries)
#This will plot the time series
abline(reg=lm(Death_df_timeseries~time(Death_df_timeseries)))
cycle(Death_df_timeseries)
#plot(aggregate(Death_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Death_df_timeseries~cycle(Death_df_timeseries))
acf(log(Death_df_timeseries))
pacf(diff(log(Death_df_timeseries)))
(fit <- arima(log(Death_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Death_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#######Q3. ###############
library(dplyr)
library(janitor)
EXPECTATION <- read.table("E:/Datasets/StatewiseTestingDetails.csv", header=T, sep=",")
head(EXPECTATION)
nrow(EXPECTATION)
EXPECTATION <- EXPECTATION[!is.na(EXPECTATION$Positive), ]
nrow(EXPECTATION)
head(EXPECTATION)
tail(EXPECTATION)
EXPECTATION <- EXPECTATION[order(EXPECTATION$Date),]
row.names(EXPECTATION) <- NULL
head(EXPECTATION)
nrow(EXPECTATION)
####################  Third Wave Prediction ###################
Positive_df <- data.frame(EXPECTATION$Date, EXPECTATION$Positive)
head(Positive_df)
tail(Positive_df)
Positive_df <- aggregate(Positive_df["EXPECTATION.Positive"], by=Positive_df["EXPECTATION.Date"], sum)
head(Positive_df)
tail(Positive_df)
#################### Based on Month using three models ###################
#Simple Movie Average
Positive_df_timeseries<-  ts(Positive_df$EXPECTATION.Positive, freq=12 ,  start=c(2020, 4), end=c(2021, 8))
head(Positive_df_timeseries)
class(Positive_df_timeseries)
Positive_df_timeseries
plot.ts(Positive_df_timeseries)
library("TTR")
Positive_df_timeseries_SMA <- SMA(Positive_df_timeseries,n=1)
Positive_df_timeseries_SMA
plot.ts(Positive_df_timeseries_SMA)
#Exponential Smoothing 
Positive_smooth <- HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE)
Positive_smooth$fitted
plot(Positive_smooth)
Positive_smooth$SSE
HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Positive_forcast <- forecast:::forecast.HoltWinters(Positive_smooth, h=8)
Positive_forcast
# Arima :-
plot(Positive_df_timeseries)
#This will plot the time series
abline(reg=lm(Positive_df_timeseries~time(Positive_df_timeseries)))
cycle(Positive_df_timeseries)
#plot(aggregate(Positive_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Positive_df_timeseries~cycle(Positive_df_timeseries))
acf(log(Positive_df_timeseries))
pacf(diff(log(Positive_df_timeseries)))
(fit <- arima(log(Positive_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 1*12)
pred
ts.plot(Positive_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))
#################### Based on Week using three models ###################
#Simple Movie Average
Positive_df_timeseries<-  ts(Positive_df$EXPECTATION.Positive, freq=52 ,  start=c(2020, 4), end=c(2021, 8))
head(Positive_df_timeseries)
class(Positive_df_timeseries)
Positive_df_timeseries
plot.ts(Positive_df_timeseries)
library("TTR")
Positive_df_timeseries_SMA <- SMA(Positive_df_timeseries,n=1)
Positive_df_timeseries_SMA
plot.ts(Positive_df_timeseries_SMA)
#Exponential Smoothing 
Positive_smooth <- HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE)
Positive_smooth$fitted
plot(Positive_smooth)
Positive_smooth$SSE
HoltWinters(Positive_df_timeseries, beta=FALSE, gamma=FALSE, l.start=23.56)
library("forecast")
Positive_forcast <- forecast:::forecast.HoltWinters(Positive_smooth, h=8)
Positive_forcast
# Arima :-
plot(Positive_df_timeseries)
#This will plot the time series
abline(reg=lm(Positive_df_timeseries~time(Positive_df_timeseries)))
cycle(Positive_df_timeseries)
#plot(aggregate(Positive_df_timeseries,FUN=mean))
#This will aggregate the cycles and display a year on year trend
boxplot(Positive_df_timeseries~cycle(Positive_df_timeseries))
acf(log(Positive_df_timeseries))
pacf(diff(log(Positive_df_timeseries)))
(fit <- arima(log(Positive_df_timeseries), c(0, 1, 1),seasonal = list(order = c(0, 1, 1), period = 12)))
pred <- predict(fit, n.ahead = 8*7)
pred
ts.plot(Positive_df_timeseries,2.718^pred$pred, log = "y", lty = c(1,3))












```
