---
title: "lab7"
author: "utplakshi"
date: "13/10/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r, echo=TRUE}
defaultW <- getOption("warn") 
options(warn = -1) 
options(warn = defaultW)
```

## CLASS WORK

```{r, echo=TRUE}
library(igraph)
g<-graph.empty(n=10,directed=TRUE)
plot(g)
g<-graph.full(n=10,directed = FALSE,loops = FALSE)
plot(g)
g<-graph.star(n=10,mode = "out")
plot(g)
g<-graph.star(n=10,mode="in")
plot(g)
g<-graph.ring(n=10)
plot(g)
edges<-c(1,2, 3,2, 2,4)
g<-graph(edges, n=max(edges), directed=TRUE)
plot(g)
vcount(g)
ecount(g)
neighbors(g, V(g)[1], mode = 1)
incident(g,V(g)[2], mode=c("all", "out", "in", "total"))
are.connected(g,V(g)[1],V(g)[3])
m<-get.adjacency(g)
m
```

## Activity
Note: Install and import the igraph package in R and Assume your own dataset (may be 
downloaded) wherever necessary.
1. Read the given adjacency matrix into R (adjacency.csv )
2. Read the given edge matrix into R(edges.csv)
3. Create and plot the graph from the adjacency matrix and edge matrix (customize the vertex 
color edge size, vertex frame and label)
4. Display the edges & vertices, the network as matrix and the names of vertices
5. Find the count of vertices and edges of the created graph
6. Display the adjacency vertices of each vertex(individual) in the created graph
7. Find the min and max degree of the created graph
8. Create & set vertex attribute property named profit and values("+", "-", "+", "-", "+", "-", 
"+", "-", "+")
9. Create & set vertex attribute property named type and values(either leap or non-leap year)
10. Create & set edge attribute named weight and values (if edge exits in between leap year 
vertices then 5 else 1 )
11. Convert the created un-directed graph into directed graph based on the following rule
a. edge directed towards high value vertex
b. if any one of the vertex is leap year then put the reverse edge with same weight.
12. Display the adjacency matrix of the resultant directed graph.
13. Display the in-degree and out-degree of each vertex of resultant directed graph

```{r, echo=TRUE}
###############################Questions########################################
library(igraph)
library(dplyr)
# Read in CSV files with edge and node attributes
original_edgelist <- read.csv("E:/Datasets/Lab7-DataSet_Edges.csv", stringsAsFactors = FALSE)
original_edgelist
original_nodelist <- read.csv("E:/Datasets/Lab7-DataSet_Adjacency.csv", stringsAsFactors = FALSE)
original_nodelist

# Create iGraph object
graph <- graph.data.frame(original_edgelist, directed = FALSE, vertices = original_nodelist)
plot(graph)
graph <- graph.data.frame(original_edgelist, directed = TRUE, vertices = original_nodelist)
plot(graph)
# Calculate various network properties, adding them as attributes
# to each node/vertex
V(graph)$comm <- membership(optimal.community(graph))
V(graph)$comm
#V(graph)$degree <- degree(graph)
#V(graph)$degree
#V(graph)$closeness <- centralization.closeness(graph)$res
#V(graph)$closeness 
V(graph)$betweenness <- centralization.betweenness(graph)$res
V(graph)$betweenness
V(graph)$eigen <- centralization.evcent(graph)$vector
V(graph)$eigen
E(graph)$color="red"
E(graph)$width=1
plot(graph, layout=layout.circle, edge.width=E(graph)$width, edge.color= E(graph)$color, main = "Graph using igraph")
#Display the vertices of the graph
V(graph)
#Display the edges of the graph
E(graph)
#network as matrix
get.adjacency(graph)
#name of the vertices
V(graph)
#count number of edges and vertices
vcount(graph)
ecount(graph)
vcount(graph)==ecount(graph)
#adjacency vertex of each vertex
m<-as.matrix(graph)
m
adjacent_vertices(graph, V(graph), mode = c("out", "in", "all", "total"))
#Vertex with maximum degree
V(graph)$name[igraph::degree(graph)==max(igraph::degree(graph))]
#Vertex with minimum degree
V(graph)$name[igraph::degree(graph)==min(igraph::degree(graph))]
#converting the undirected graph into directed graph
graph <- graph.data.frame(original_edgelist, directed = TRUE, vertices = original_nodelist)
plot(graph)
#displaying the adjacency matrix
get.adjacency(graph)
#Displaying in and out degree of the directed graph
igraph::degree(graph)
igraph::degree(graph,mode="in")
igraph::degree(graph,mode="out")
###############PLOTTING THE GRAPHS SEPARATELY AND FINDING THE ANSWERS###########
#1. Read the adjancency matrix
adj <- read.csv("E:/Datasets/Lab7-DataSet_Adjacency.csv",  sep=",", row.names = 1, check.names = FALSE)
adj
# 2. Read the given edge matrix into R(edges.csv)
edg <- read.csv("E:/Datasets/Lab7-DataSet_Edges.csv")
edg
#3. Create and plot the graph from the adjacency matrix and edge matrix (customize the vertex
#color edge size, vertex frame and label)
# For adj data set
m <- as.matrix(adj)
m
#4. Plotting a graph for adjancency matrix
new_adj <- graph.adjacency(m,mode ="directed",weighted=NULL, diag=FALSE)
E(new_adj)$width <-1
E(new_adj)$color <-"darkolivegreen4"
plot(new_adj, edge.width = E(new_adj)$width, edge.arrow.size=0.5,
     layout= layout.fruchterman.reingold, edge.color= E(new_adj)$color)
# For Edge dataset
new_edg <- graph.data.frame(edg, directed = TRUE)
E(new_edg)$width <- 1
E(new_edg)$color <- "seagreen3"
plot(new_edg, edge.width = E(new_edg)$width ,edge.arrow.size=0.5,
     layout=layout.fruchterman.reingold, edge.color =E(new_edg)$color)
# 4. Display the edges & vertices, the network as matrix and the names of vertices
# For ADJ dataset
V(new_adj)
E(new_adj)
get.adjacency(new_adj)
V(new_adj)$name
V(new_edg)
E(new_edg)
get.adjacency(new_edg)
V(new_edg)$name
vcount(new_adj)
ecount(new_adj)
vcount(new_edg)
ecount(new_edg)
#5. Display the adjacency vertices of each vertex(individual) in the created graph
# For ADJ dataset
for (v in V(new_adj)$name)
{
  print(adjacent_vertices(new_adj, v, mode = c("out","in","all","total")))
}
# For Edge dataset

for (v in V(new_edg)$name)
{
  print(adjacent_vertices(new_adj, v, mode = c("out","in","all","total")))
}
max(igraph::degree(new_adj))
min(igraph::degree(new_adj))
max(igraph::degree(new_edg))
min(igraph::degree(new_edg))
#Create & set vertex attribute property named profit and values("+", "-", "+", "-", "+", "-",
#"+", "-", "+")
new_edg <- set_vertex_attr(new_edg, 'profit', value = c("+", "-", "+", "-", "+", "-","+", "-", "+"))
vertex_attr(new_edg)
#Create & set vertex attribute property named type and values(either leap or non-leap year)
new_edg <- set_vertex_attr(new_edg, 'Leap Year', value = c(1,0,0,0,1,0,1,0,0))                           
vertex_attr(new_edg)    
#Create & set edge attribute named weight and values (if edge exits in between leap year
#vertices then 5 else 1 )
new_edg <- set_edge_attr(new_edg, 'weight value', value = c(5,5,5,1,5,1,1,5,1))
edge_attr(new_edg)
#Convert the created un-directed graph into directed graph based on the following rule
#a. edge directed towards high value vertex
#b. if any one of the vertex is leap year then put the reverse edge with same weight.
new_adj = as.directed(new_adj)
plot(new_adj,edge.arrow.size=0.5, vertex.color="blue",vertex.size=15,
     vertex.frame.color="black",vertex.label.color="red",
     vertex.label.cex=0.8, vertex.label.dist=2, edge.curved=0.2)
#Display the in-degree and out-degree of each vertex of resultant directed graph
igraph::degree(new_adj,mode="in")
igraph::degree(new_adj,mode="out")
igraph::degree(new_adj)

```

##### You reached to the end of the document, knit the worked out document into html format and uplaod the html file. 
```{r, echo=TRUE}
print(Sys.time())
print(Sys.getenv("COMPUTERNAME"))
print(Sys.getenv("USERNAME"))
```